---
title: "R Notebook"
output: html_notebook
fig_height: 200
---

## Import library

```{r}
library(tidyverse)
library(ggplot2)
library(gridExtra)
```

## Read file

```{r}
df = read.csv('../dataset/cleaned/cleaned_data_no_outlier_label.csv')

head(df, 5)
```

```{r}

prepare.df.by.category = function(cat){
  
  data.by.cat = df %>% select('assignment_gs_correct_count',  'assignment_gs_count', 'assignment_price', 'microtasks_count', 'completion.time.in.minutes', cat)
  
  data.by.cat = data.by.cat %>% 
  pivot_longer(cols=c('assignment_gs_correct_count',  'assignment_gs_count', 'assignment_price', 'microtasks_count'), names_to = 'parameter')
  
  return(data.by.cat)
}
```


```{r fig.width=10, fig.height=3.5}
df2 = prepare.df.by.category('device_category')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=device_category)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by device type') + 
  theme(
    strip.text = element_text(size = 10),
    axis.title.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```

The above graph shows scatter plot of `assignment_gs_correct_count`,  `assignment_gs_count`, `assignment_price` and `microtasks_count` against completion time by device category.

The graph shows that regardless device category; `assignment_gs_correct_count`,  `assignment_gs_count`, `assignment_price` and `microtasks_count` do not correlate with the completion time.

<br/>


```{r fig.width=10, fig.height=3}
df2 = prepare.df.by.category('assignment_type')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=assignment_type)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by assignment type') + 
  theme(
    strip.text = element_text(size = 10),
    axis.title.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```

The above graph shows scatter plot of `assignment_gs_correct_count`,  `assignment_gs_count`, `assignment_price` and `microtasks_count` against completion time by assignment type.

The graph shows that regardless assignment type; `assignment_gs_correct_count`,  `assignment_gs_count` and `microtasks_count` do not correlate with the completion time. In contrast, for the *exam* assignment type, the higher `assignment_price` correlates with low completion time.

<br/>

```{r fig.height=3}
df2 = prepare.df.by.category('project_instruction_language')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=project_instruction_language)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by instruction language') + 
  theme(
    strip.text = element_text(size = 5),
    axis.title.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```
The above graph shows scatter plot of `assignment_gs_correct_count`,  `assignment_gs_count`, `assignment_price` and `microtasks_count` against completion time by project instruction language.

The graph shows that regardless project instruction language; `assignment_gs_correct_count`,  `assignment_gs_count` and `microtasks_count` do not correlate with the completion time. In contrast, for the *ru* project instruction, the higher `assignment_price` correlates with low completion time.

<br/>



```{r fig.width=10, fig.height=8}

prepare.df.by.category = function(cat){
  
  data.by.cat = df %>% select(project_has_audio, project_has_externalHtml, project_has_fileAudio_input, project_has_fileImg_input, project_has_file_input, project_has_iframe, project_has_sbs, project_has_select_input, project_has_sourcesRecorder_input, project_has_suggest_input, project_has_textarea_input, project_has_video, cat, completion.time.in.minutes)
  
  data.by.cat = data.by.cat %>% 
  pivot_longer(cols=c('project_has_audio', 'project_has_externalHtml', 'project_has_fileAudio_input', 'project_has_fileImg_input', 'project_has_file_input', 'project_has_iframe', 'project_has_sbs', 'project_has_select_input', 'project_has_sourcesRecorder_input', 'project_has_suggest_input', 'project_has_textarea_input', 'project_has_video'), names_to = 'parameter')
  
  return(data.by.cat)
}

```


```{r fig.width=10, fig.height=8}
df2 = prepare.df.by.category('device_category')

plt = df2 %>% ggplot(aes(x=factor(value), y=completion.time.in.minutes, color=device_category)) +
  geom_boxplot() +
  facet_wrap(vars(parameter), nrow=4, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by assignment status') + 
  theme(
    strip.text = element_text(size = 12),
    axis.text.x = element_text(size=15),
    axis.text.y = element_text(size = 15),
    legend.position = 'bottom'
  )

plt
```
The above graph shows boxplots of project attribute (i.e., `has_audio`, `has_button`, `has_checkbox_input`, `has_externalHtml`, `has_fileAudio_input`, `has_fileImg_input`, `has_fileVideo_input`, `has_file_input`, `has_iframe`, `has_image`, `has_radio_input`, `has_sbs`, `has_select_input`, `has_sourcesRecorder_input`, `has_string_input`, `has_suggest_input`, `has_textarea_input`, `has_video`) against project completion time by device category.

Overall, the graph shows that 
- the higher number of these attributes correlates with longer project completion time.
- the variety of device categories that assignments are taken has inverse relationship with the number of these attributes (e.g., assignments are done in 5 device categories when project does not have suggested input, while assignments are done in 2 device categories when project has 32 suggested input).

<br/>

```{r fig.width=10, fig.height=8}
df2 = prepare.df.by.category('assignment_type')

plt = df2 %>% ggplot(aes(x=factor(value), y=completion.time.in.minutes, color=assignment_type)) +
  geom_boxplot() +
  facet_wrap(vars(parameter), nrow=4, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by assignment status') + 
  theme(
    strip.text = element_text(size = 12),
    axis.text.x = element_text(size=15),
    axis.text.y = element_text(size = 15),
    legend.position = 'bottom'
  )

plt
```
The above graph shows boxplots of project attribute (i.e., `has_audio`, `has_button`, `has_checkbox_input`, `has_externalHtml`, `has_fileAudio_input`, `has_fileImg_input`, `has_fileVideo_input`, `has_file_input`, `has_iframe`, `has_image`, `has_radio_input`, `has_sbs`, `has_select_input`, `has_sourcesRecorder_input`, `has_string_input`, `has_suggest_input`, `has_textarea_input`, `has_video`) against project completion time by assignment type.

Overall, the graph shows that regardless assignment type, the higher number of these attributes correlates with longer project completion time.

<br/>

```{r fig.width=10, fig.height=8}
df2 = prepare.df.by.category('project_instruction_language')

plt = df2 %>% ggplot(aes(x=factor(value), y=completion.time.in.minutes, color=project_instruction_language)) +
  geom_boxplot() +
  facet_wrap(vars(parameter), nrow=4, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by assignment status') + 
  theme(
    strip.text = element_text(size = 12),
    axis.text.x = element_text(size=15),
    axis.text.y = element_text(size = 15),
    legend.position = 'bottom'
  )

plt
```
The above graph shows boxplots of project attribute (i.e., `has_audio`, `has_button`, `has_checkbox_input`, `has_externalHtml`, `has_fileAudio_input`, `has_fileImg_input`, `has_fileVideo_input`, `has_file_input`, `has_iframe`, `has_image`, `has_radio_input`, `has_sbs`, `has_select_input`, `has_sourcesRecorder_input`, `has_string_input`, `has_suggest_input`, `has_textarea_input`, `has_video`) against project completion time by instruction language.

Overall, the graph shows that regardless instruction language, the higher number of these attributes correlates with longer project completion time.

<br/>

```{r}
prepare.df.by.category = function(cat){

  data.by.cat = df %>% 
    select(project_instruction_FK, project_instruction_len, project_instruction_wordCount, project_required_fields, project_spec_length, completion.time.in.minutes, cat)
  
  data.by.cat = data.by.cat %>% 
    pivot_longer(cols=c('project_instruction_FK', 'project_instruction_len', 'project_instruction_wordCount', 'project_required_fields', 'project_spec_length'), names_to = 'parameter')
  
  return(data.by.cat)
}

```


```{r fig.height=3.5, fig.width=10}
df2 = prepare.df.by.category('device_category')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=device_category)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by device type') + 
  theme(
    strip.text = element_text(size = 8),
    axis.text.x = element_text(size=8, angle = 30),
    axis.text.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```
The above graph shows scatter plot of `project_instruction_FK`, `project_instruction_len`, `project_instruction_wordCount`, `project_required_fields`, and `project_spec_length` against completion time by device category.

The graph shows that regardless device categories; `project_instruction_FK`, `project_instruction_len`, `project_instruction_wordCount`, `project_required_fields`, and `project_spec_length` do not correlate with the completion time.

<br/>

```{r fig.height=3.5, fig.width=10}
df2 = prepare.df.by.category('assignment_type')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=assignment_type)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by assignment type') + 
  theme(
    strip.text = element_text(size = 8),
    axis.text.x = element_text(size=8, angle = 30),
    axis.text.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```
The above graph shows scatter plot of `project_instruction_FK`, `project_instruction_len`, `project_instruction_wordCount`, `project_required_fields`, and `project_spec_length` against completion time by assignment type.

The graph shows that regardless assignment type; `project_instruction_FK`, `project_instruction_len`, `project_instruction_wordCount`, `project_required_fields`, and `project_spec_length` do not correlate with the completion time.

<br/>

```{r fig.height=3.5, fig.width=10}
df2 = prepare.df.by.category('project_instruction_language')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=project_instruction_language)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by instruction language') + 
  theme(
    strip.text = element_text(size = 8),
    axis.text.x = element_text(size=8, angle = 30),
    axis.text.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```
The above graph shows scatter plot of `project_instruction_FK`, `project_instruction_len`, `project_instruction_wordCount`, `project_required_fields`, and `project_spec_length` against completion time by instruction language.

The graph shows that regardless instruction language; `project_instruction_FK`, `project_instruction_len`, `project_instruction_wordCount`, `project_required_fields`, and `project_spec_length` do not correlate with the completion time.

<br/>

```{r}
prepare.df.by.category = function(cat){
  
  data.by.cat = df %>% select(project_has_button,  project_has_checkbox_input, project_has_image, project_has_radio_input, project_has_string_input, completion.time.in.minutes, cat)
  
  data.by.cat = data.by.cat %>% 
    pivot_longer(cols=c('project_has_button',  'project_has_checkbox_input', 'project_has_image', 'project_has_radio_input', 'project_has_string_input'), names_to = 'parameter')
  
  return(data.by.cat)
}

```


```{r fig.height=3.5, fig.width=10}
df2 = prepare.df.by.category('device_category')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=device_category)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by device type') + 
  theme(
    strip.text = element_text(size = 8),
    axis.text.x = element_text(size=8, angle = 30),
    axis.text.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```
The above graph shows scatter plot of `project_has_button`,  `project_has_checkbox_input`, `project_has_image`, `project_has_radio_input`, and  `project_has_string_input` against completion time by device category.

The graph shows that regardless device categories; `project_has_button`,  `project_has_checkbox_input`, `project_has_image`, `project_has_radio_input`, and  `project_has_string_input` do not correlate with the completion time.

<br/>

```{r fig.height=3.5, fig.width=10}
df2 = prepare.df.by.category('assignment_type')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=assignment_type)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by assignment type') + 
  theme(
    strip.text = element_text(size = 8),
    axis.text.x = element_text(size=8, angle = 30),
    axis.text.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```
The above graph shows scatter plot of `project_has_button`,  `project_has_checkbox_input`, `project_has_image`, `project_has_radio_input`, and  `project_has_string_input` against completion time by assignment type.

The graph shows that regardless assignment types; `project_has_button`,  `project_has_checkbox_input`, `project_has_image`, `project_has_radio_input`, and  `project_has_string_input` do not correlate with the completion time.

<br/>

```{r fig.height=3.5, fig.width=10}
df2 = prepare.df.by.category('project_instruction_language')

plt = df2 %>% ggplot(aes(x=value, y=completion.time.in.minutes, color=project_instruction_language)) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(parameter), nrow=1, scales = "free_x") +
  xlab('') + ylab('completion time (in minute)') + 
  ggtitle('plot by instruction language') + 
  theme(
    strip.text = element_text(size = 8),
    axis.text.x = element_text(size=8, angle = 30),
    axis.text.y = element_text(size = 8),
    legend.position = 'bottom'
  )

plt
```

The above graph shows scatter plot of `project_has_button`,  `project_has_checkbox_input`, `project_has_image`, `project_has_radio_input`, and  `project_has_string_input` against completion time by instruction language.

The graph shows that regardless instruction language; `project_has_button`,  `project_has_checkbox_input`, `project_has_image`, `project_has_radio_input`, and  `project_has_string_input` do not correlate with the completion time.

<br/>